---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
library(subsetr)
```
# subsetr

subsetr uses tidy evaluation principles developed in rlang to provide
`subset.data.frame()` and `[.data.frame()` methods which use tidy non-standard
evaluation.

For most cases they provide drop in replacements for the existing methods, but
can also avoid repetitive subsetting code. Because rlang provides robust
lexical scoping they are suitable for use in top level scripts, functions and
packages.

## Examples

```{r}
# Most existing code will work identically
mtcars[mtcars$hp > 250, "mpg"]

# But you can also use NSE to make things simpler
mtcars[hp > 250, mpg]

# The `j` argument works the same as the `select` argument in `base::subset()`.
mtcars[hp > 250, mpg:disp]

mtcars[hp > 250, -mpg]
```

The `subset()` interface is identical, but it now can also work properly inside
all functions.
```{r}
detach(package:subsetr)
val <<- 400
f <- function(x, val) {
  lapply(x, subset, hp > val)
}
f(list(mtcars), 250)

library(subsetr)
f <- function(x, val) {
  lapply(x, subset, hp > val)
}
f(list(mtcars), 250)
```
